Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation

### 2024-01-25 draft/ms-adj-draft.Rmd
before figure overhaul

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: no
    number_sections: no
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
always_allow_html: true
header-includes:
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
#- \setlength{\headheight}{14.5pt}
#- \setlength{\headheight}{13.6pt}
# - \usepackage{fancyhdr}
# - \pagestyle{fancy}
# - \lhead{N.I. Hoffmann}
# - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
# - \newcommand{\beginsupplement}{\setcounter{table}{0}  
# \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} 
# \renewcommand{\thefigure}{A\arabic{figure}}}

@@

title: "Demystifying Double Robust, Flexible Adjustment Methods for Causal Inference"
#subtitle: "PAA 2023"
author:  Nathan I. Hoffmann
#   | Department of Sociology, UCLA
date: "`r format(Sys.time(), '%B %e, %Y')`"

abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years. Despite their apparent advantages, these methods remain underutilized by social scientists. It is also unclear whether these methods actually outperform more traditional methods in finite samples. This paper has two aims: it is a guide to some of the latest methods in doubly robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods. It does this by using both simulated data where the treatment effect estimate is known, and then using complex survey data from the Program for International Student Assessment (PISA). Methods covered include Targeted Maximum Likelihood Estimation, Double/Debiased Machine Learning, and Augmented Inverse Propensity Weighting. Although these methods are robust to either the exposure or response model being misspecified, preliminary results show that, when both models are incorrect, bias grows rapidly in small samples."

@@

library(broom)
library(knitr)
library(here)
library(haven)
library(tidyverse)

@@

```{r, functions}
perform <- function(est_df, label){
  est_df %>%
    summarize(bias = mean(d - truth),
              percent_bias = bias/sd(d),
              rmse = sqrt(mean(d - truth)^2),
              mae = median(abs(d - truth)),
              fail_count = first(fail_count),
              comp_time = first(comp_time)) %>%
    mutate(label = label,
           n = nrow(est_df) + fail_count) %>%
    select(label, everything()) %>%
    return()
}
```

```{r load, eval = F}
# data from mx0.5
pisa <- readRDS('/Users/nathan/My Drive/1 UCLA/Dissertation/data/pisa.rds') %>%
  mutate(age = as.numeric(age))

pisa <- pisa %>%
  filter(across(c(female,  mom_ed, dad_ed, early_ed, cultural_pos, home_ed, age,
                  math1, math2, math3, math4, math5,
                  read1, read2, read3, read4, read5,
                  scie1, scie2, scie3, scie4, scie5),
                ~ !is.na(.x))) %>%
  mutate(
    country = case_when(
       country == '034400' ~ 'Hong Kong',
       country == '044600'~ 'Macao',
       country == 'Russian Federation' ~ 'Russia',
       country == 'United States of America' ~ 'United States',
       T ~ country
     ),
   birth_country = case_when(
       birth_country == '034400' ~ 'Hong Kong',
       birth_country == '044600'~ 'Macao',
       birth_country == 'United States of America' ~ 'United States',
       T ~ birth_country
     ),
   immigrant = case_when(
    birth_country != country ~ T,
    birth_country == country ~ F
    )) %>%
  # include immigrants with a birth country in the dataset, or non-immigrants
  filter((immigrant == T & birth_country %in% unique(pisa$country)) | 
           immigrant == F) %>%
   mutate(school_id = paste0(year, school_id),
         village = school_location == 'Village',
         non_urban = ifelse(!is.na(school_location), school_location %in% c('Village', 'Small Town', 'Town'), NA),
         match_country = ifelse(immigrant == T, birth_country, country))

# Include only match_country with at least 5 imm and 5 non-imm
n_min <- 5
match_country_imm <- pisa %>%
  filter(immigrant == T) %>%
  group_by(match_country) %>%
  count() %>% 
  filter(n >= n_min) %>%
  pull(match_country)

match_country_nonimm <- pisa %>%
  filter(immigrant == F) %>%
  group_by(match_country) %>%
  count() %>% 
  filter(n >= n_min) %>%
  pull(match_country)

pisa <- pisa %>%
  filter(match_country %in% match_country_imm,
         match_country %in% match_country_nonimm,
         # Remove match_country with no immigrants
         match_country %in% unique(pisa$match_country[pisa$immigrant == T])
         ) %>%
  mutate(immigrant = as.numeric(immigrant))
```

>>>>

---
output:
  # bookdown::word_document2:
    # reference_docx: "word-template.docx"
  bookdown::pdf_document2:
    toc: no
    number_sections: yes
    pandoc_args: !expr rmdfiltr::add_wordcount_filter(rmdfiltr::add_citeproc_filter(args = NULL))
    latex_engine: xelatex
always_allow_html: true
header-includes:
  #- \usepackage{setspace}\doublespace
  # - \usepackage[nolists, fighead, tabhead]{endfloat}
  # - \usepackage{endnotes}
  # - \let\footnote=\endnote
  # - \setlength{\headheight}{14.5pt}
  # - \setlength{\headheight}{13.6pt}
  - \usepackage{fancyhdr}
  - \pagestyle{fancy}
  - \lhead{N.I. Hoffmann}
  - \rhead{`r format(Sys.time(), '%B %e, %Y')`}
# - \newcommand{\beginsupplement}{\setcounter{table}{0}  
# \renewcommand{\thetable}{A\arabic{table}} \setcounter{figure}{0} 
# \renewcommand{\thefigure}{A\arabic{figure}}}

@@

title: "Double Robust, Flexible Adjustment Methods for Causal Inference: An Overview and an Evaluation"
# subtitle: "American Sociological Association Annual Meeting 2024"
author:  Nathan I. Hoffmann, Department of Sociology, UCLA
date: "`r format(Sys.time(), '%B %e, %Y')`"

abstract: "Double robust methods for flexible covariate adjustment in causal inference have proliferated in recent years. Despite their apparent advantages, these methods remain underutilized by social scientists. It is also unclear whether these methods actually outperform more traditional methods in finite samples. This paper has two aims: It is a guide to some of the latest methods in double robust, flexible covariate adjustment for causal inference, and it compares these methods to more traditional statistical methods. It does this by using both simulated data where the treatment effect estimate is known, and then using comparisons of experimental and observational data from the National Supported Work Demonstration. Methods covered include Augmented Inverse Probability Weighting, Targeted Maximum Likelihood Estimation, and Double/Debiased Machine Learning. Results suggest that these methods do not necessarily outperform OLS regression or matching on propensity score estimated by logistic regression, even in cases where the data generating process is not linear."

@@

library(SuperLearner)
library(broom)
library(knitr)
library(kableExtra)
library(here)
library(haven)
library(tidyverse)

@@

```{r load}

unemp_func <- function(x){
  x %>%
    as.data.frame() %>%
    mutate(re74_0 = re74 == 0,
         re75_0 = re75 == 0) 
}

```{r load-sims, eval = F}
lalonde_bootstrap <- function(dataset, sample, include_74 = F, iter = 100){

  lalonde_variables <- c('age', 'education', 'black', 'hispanic', 'married', 'nodegree', 're75', 're75_0')
  if(include_74 == F){
        dataset <- bind_rows(filter(lalonde_exp, treat == 1), dataset)

      } else {
        lalonde_variables <- c(lalonde_variables, 're74', 're74_0')
        dataset <- bind_rows(filter(lalonde_exp_74, treat == 1), dataset)
      }

  bootstrap_list <- list()

  for(i in 1:iter){
    dataset_bootstrap <- sample_n(dataset, nrow(dataset), replace = T)

    bootstrap_list[[i]] <- list(y = dataset_bootstrap$re78,
                  z = ifelse(dataset_bootstrap$treat == 1, 'trt', 'ctl'),
                  x = dataset_bootstrap[,lalonde_variables],
                  y.1 = NA, y.0 = NA,
                  dataset = i,
                  set = sample,
                  size = nrow(dataset_bootstrap))
  }

  return(bootstrap_list)
}

set.seed(1859)
sims_lalonde <- c(
  lalonde_bootstrap(filter(lalonde_exp, treat == 0), sample = 'lalonde experimental original'),
  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 original'),
  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 original'),
  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 original'),
  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 original'),
  lalonde_bootstrap(filter(lalonde_exp_74, treat == 0), sample = 'lalonde experimental 74', include_74 = T),
  lalonde_bootstrap(lalonde_psid1_controls, 'lalonde PSID-1 74', include_74 = T),
  lalonde_bootstrap(lalonde_psid3_controls, 'lalonde PSID-3 74', include_74 = T),
  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-1 74', include_74 = T),
  lalonde_bootstrap(lalonde_cps1_controls, 'lalonde CPS-3 74', include_74 = T))

# sims <- readRDS(here('files', 'sims.RDS'))

sims_main <- readRDS(here('files_main', 'sims.RDS'))
sims_large <- readRDS(here('files_large', 'sims_large.RDS'))
sims_small <- readRDS(here('files_small', 'sims_small.RDS'))

sims <- sims_main %>% append(sims_small) %>% append(sims_large) %>% append(sims_lalonde)

# sims <- sims %>% append(sims_large)

# sims <- readRDS(here('files', 'sims_small.RDS'))

# for(i in 1:length(sims_small)){
#   # sims_large[[i]]$size <- nrow(sims_large[[i]]$x)
#   sims_small[[i]]$dataset <- 7
# }
# saveRDS(sims_large, here('files_large', 'sims_large.RDS'))
# 
# 
# sims_combined <- sims %>% append(sims_small) %>% append(sims_large)
# 
# index_df <- data.frame(dorie_dataset = sapply(sims_combined, function(x) x$dataset),
#                        set = sapply(sims_combined, function(x) x$set),
#                        size = sapply(sims_combined, function(x) x$size)) %>%
#   mutate(dataset = c(1:length(sims), 1:length(sims_small), 1:length(sims_large)))
# 
# lm_df <- read_csv(here('files_main', 'lm_df.csv')) %>% 
#   mutate(set = c(rep('main', 200), rep('linear', 200))) %>%
#   bind_rows(read_csv(here('files_small', 'lm_df.csv')) %>% mutate(set = 'small')) %>%
#   bind_rows(read_csv(here('files_large', 'lm_df.csv')) %>% mutate(set = 'large')) %>%
#   left_join(index_df)
# 
# 
# write_csv(lm_df, here('files', 'lm_df.csv'))
# 
# psm_df <- read_csv(here('files_main', 'psm_df.csv')) %>% 
#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
#   bind_rows(read_csv(here('files_small', 'psm_df.csv')) %>% mutate(set = 'small')) %>%
#   bind_rows(read_csv(here('files_large', 'psm_df.csv')) %>% mutate(set = 'large')) %>%
#   left_join(index_df)
# 
# write_csv(lm_df, here('files', 'psm_df.csv'))
# 
# 
# aipw_df <- read_csv(here('files_main/homemade', 'aipw.csv')) %>% 
#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'aipw.csv')) %>% mutate(set = 'small')) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'aipw.csv')) %>% mutate(set = 'large')) %>%
#   left_join(index_df)
# 
# write_csv(aipw_df, here('files/homemade', 'aipw.csv'))
# 
# 
# aipw_trunc_df <- read_csv(here('files_main/homemade', 'aipw_trunc.csv')) %>% 
#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'small')) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'aipw_trunc.csv')) %>% mutate(set = 'large')) %>%
#   left_join(index_df)
# 
# write_csv(aipw_trunc_df, here('files/homemade', 'aipw_trunc.csv'))
# 
# tmle_df <- read_csv(here('files_main/homemade', 'tmle.csv')) %>% 
#   mutate(set = ifelse(dataset <= 200, 'main', 'linear')) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'tmle.csv')) %>% mutate(set = 'small')) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'tmle.csv')) %>% mutate(set = 'large')) %>%
#   left_join(index_df)
# 
# write_csv(tmle_df, here('files/homemade', 'tmle.csv'))
# 
# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   left_join(index_df) 
# 
# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
# 
# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   select(-dorie_dataset) %>%
#   left_join(index_df)
# 
# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
# 
# 
# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   select(-dorie_dataset) %>%
#   left_join(index_df)
# 
# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))

# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
# 
# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
# 
# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
# 
# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))

# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
# 
# dml_ols_logit %>%
#   filter(set == 'main') %>%
#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
# 
# dml_ols_logit %>%
#   filter(set == 'large') %>%
#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))

## add lalonde ####
# read_csv(here('files_combined', 'lm_df.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde', 'lm_df.csv'))) %>%
#   write_csv(here('files', 'lm_df.csv'))
# 
# 
# read_csv(here('files_combined', 'psm_df.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde', 'psm_df.csv'))) %>%
#   write_csv(here('files', 'psm_df.csv'))
# 
# read_csv(here('files_combined', 'lin.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde', 'lin.csv'))) %>%
#   write_csv(here('files', 'lin.csv'))
# 
# read_csv(here('files_combined', 'gcomp.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde', 'gcomp.csv'))) %>%
#   write_csv(here('files', 'gcomp.csv'))
# 
# read_csv(here('files_combined/homemade', 'aipw.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw.csv'))) %>%
#   write_csv(here('files/homemade', 'aipw.csv'))
# 
# read_csv(here('files_combined/homemade', 'aipw_trunc.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'aipw_trunc.csv'))) %>%
#   write_csv(here('files/homemade', 'aipw_trunc.csv'))
# 
# read_csv(here('files_combined/homemade', 'tmle.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'tmle.csv'))) %>%
#   write_csv(here('files/homemade', 'tmle.csv'))
# 
# read_csv(here('files_combined/homemade', 'dml_ols_logit.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_ols_logit.csv'))) %>%
#   write_csv(here('files/homemade', 'dml_ols_logit.csv'))
# 
# read_csv(here('files_combined/homemade', 'dml_grf.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_grf.csv'))) %>%
#   write_csv(here('files/homemade', 'dml_grf.csv'))
# 
# read_csv(here('files_combined/homemade', 'dml_superlearner.csv')) %>%
#   bind_rows(read_csv(here('files_lalonde/homemade', 'dml_superlearner.csv'))) %>% 
#   write_csv(here('files/homemade', 'dml_superlearner.csv'))
# 
# 
# readRDS(here('files_combined/homemade', 'ols_logit_pred.RDS')) %>%
#   bind_rows(readRDS(here('files_lalonde/homemade', 'ols_logit_pred.RDS'))) %>%
#   saveRDS(here('files/homemade', 'ols_logit_pred.RDS'))
# 
# readRDS(here('files_combined/homemade', 'grf_pred.RDS')) %>%
#   bind_rows(readRDS(here('files_lalonde/homemade', 'grf_pred.RDS'))) %>%
#   saveRDS(here('files/homemade', 'grf_pred.RDS'))
# 
# readRDS(here('files_combined/homemade', 'superlearner_pred.RDS')) %>%
#   bind_rows(readRDS(here('files_lalonde/homemade', 'superlearner_pred.RDS'))) %>%
#   saveRDS(here('files/homemade', 'superlearner_pred.RDS'))

# dml_ols_logit_df <- read_csv(here('files_main/homemade', 'dml_ols_logit.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_ols_logit.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   left_join(index_df) 
# 
# write_csv(dml_ols_logit_df, here('files/homemade', 'dml_ols_logit.csv'))
# 
# dml_grf_df <- read_csv(here('files_main/homemade', 'dml_grf.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_grf.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_grf.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   select(-dorie_dataset) %>%
#   left_join(index_df)
# 
# write_csv(dml_grf_df, here('files/homemade', 'dml_grf.csv'))
# 
# 
# dml_superlearner_df <- read_csv(here('files_main/homemade', 'dml_superlearner.csv')) %>%
#   mutate(dataset = 1:nrow(.)) %>%
#   bind_rows(read_csv(here('files_small/homemade', 'dml_superlearner.csv')) %>% 
#               mutate(set = 'small',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   bind_rows(read_csv(here('files_large/homemade', 'dml_superlearner.csv')) %>% 
#               mutate(set = 'large',
#                      dorie_dataset = 7,
#                      dataset = row_number())) %>%
#   select(-dorie_dataset) %>%
#   left_join(index_df)
# 
# write_csv(dml_superlearner_df, here('files/homemade', 'dml_superlearner.csv'))

# ols_logit_pred_combined <- readRDS(here('files_main/homemade', 'ols_logit_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'ols_logit_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'ols_logit_pred.RDS')))
# 
# grf_pred_combined <- readRDS(here('files_main/homemade', 'grf_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'grf_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'grf_pred.RDS')))
# 
# superlearner_pred_combined <- readRDS(here('files_main/homemade', 'superlearner_pred.RDS')) %>%
#   append(readRDS(here('files_small/homemade', 'superlearner_pred.RDS'))) %>%
#   append(readRDS(here('files_large/homemade', 'superlearner_pred.RDS')))
# 
# saveRDS(ols_logit_pred_combined, here('files/homemade', 'ols_logit_pred.RDS'))
# saveRDS(grf_pred_combined, here('files/homemade', 'grf_pred.RDS'))
# saveRDS(superlearner_pred_combined, here('files/homemade', 'superlearner_pred.RDS'))

# dml_ols_logit <- read_csv(here('files_large/homemade', 'dml_ols_logit.csv')) 
# 
# dml_ols_logit %>%
#   filter(set == 'main') %>%
#   write_csv(here('files_main/homemade', 'dml_ols_logit.csv'))
# 
# dml_ols_logit %>%
#   filter(set == 'large') %>%
#   write_csv(here('files_large/homemade', 'dml_ols_logit.csv'))

```{r sim-homemade, eval = F}
sim_homemade <- function(n, m = NULL){
  if(is.null(m)){
    m <- round(n/100)
  }

  dat <- replicate(m, rnorm(n, 0, 5)) %>% 
    as.data.frame() 
  dat_original <- dat

  # first make treatment indicator
  dat <- data.frame(1, dat)
  coefs <- rnorm(m+1, 0, 2)
  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))

  dat <- data.frame(dat, d)

  # Set treatment effect to 2
  coefs <- c(rnorm(m+1, 0, 2), 2)
  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)

  dat <- data.frame(dat, y)

  dat_new <- dat_original

  transformers <- rnorm(m, 0, 2)

  for(i in 1:m){
    dat_new[,i] <- dat_new[,i] * transformers[i]
  }

  # m/4 squared terms
  dat_new <- dat_new %>% 
    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))

  # m/4 exponentiated 
  dat_new <- dat_new %>% 
    mutate(across(sample(1:m, m/4, replace = F), function(x) exp(x)))

  # m/4 sin 
  dat_new <- dat_new %>% 
    mutate(across(sample(1:m, m/4, replace = F), function(x) sin(x)))

  # m/2 2-way interactions
  for(i in 1:round(m/2)){
    index <- sample(1:m, 2, replace = F)
    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
  }

  # m/4 3-way interactions
  for(i in 1:round(m/4)){
    index <- sample(1:m, 3, replace = F)
    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
  }

  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
  return(dat_final)
}

# 500, 1000, 5000, 10k, 50k, 100k
# Set m = 1% of n
# 50 of each 
# then set n = 5000 and m = 10, 50, 200, 1000
set.seed(185)
sim_homemade_list <- list()
for(n in c(500, 1000, 5000, 1e3, 5e3, 1e5)){
  print(paste0('n = ', n))
  for(i in 1:50){
    print(i)
    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n) %>%
      mutate(n = n, m  = n/100, dataset = i, simulation = 'n')
  }
}
for(m in c(10, 50, 200, 500, 1000)){
  print(paste0('m = ', m))
  for(i in 1:50){
    print(i)
    sim_homemade_list[[paste0(n, i)]] <- sim_homemade(n = n, m = m) %>%
      mutate(n = n, m  = m, dataset = i, simulation = 'm')
  }
}

saveRDS(sim_homemade_list, here('files', 'sim_homemade.RDS'))

```{r github-datageneration, eval = F}
# from https://github.com/QuantLet/DataGenerationForCausalInference

### This generates the Simulation Data as a dataframe
# by Daniel Jacob (daniel.jacob@hu-berlin.de)

# Arguments to specify are: 
# Y = Outcome (dependend variable). Either continuous or binary. 
# N = Number of observations (real number)
# k = Number of covariates (real number). At least 10 
# random_d = treatment assignment: (Either T for random assignment or F for confounding on X)
# theta = treatment effect: (Either real number for only one theta, or "binary" {0.1,0.3}, "con" for continuous values (0.1,0.3) or "big" for {1,0.4})
# var = Size of the variance (Noise-level)

#Required Packages
if(!require("clusterGeneration")) install.packages("clusterGeneration"); library("clusterGeneration")
if(!require("mvtnorm")) install.packages("mvtnorm"); library("mvtnorm")

datagen <- function(N,y,k,random_d,theta,var) {

  N = N
  k = k
  b = 1 / (1:k)
  # = Generate covariance matrix of z = #
  sigma <- genPositiveDefMat(k, "unifcorrmat")$Sigma
  sigma <- cov2cor(sigma)

  z <- rmvnorm(N, sigma = sigma) # = Generate z = #

  ### Options for D (m_(X))
  if (random_d == T) {
    d <- rep(c(0, 1), length.out = N)
  } else {
    d_prop <- pnorm(z %*% b) # D is dependent on Za
    d <- as.numeric(rbinom(N, prob = d_prop, size = 1))
  }

  ### Options for theta
  if (theta == "con") {
    theta_s <- as.vector(sin(z %*% b) ^ 2)
    theta <-
      (theta_s - min(theta_s)) * (0.3 - 0.1) / (max(theta_s) - min(theta_s)) +
      0.1
  } else if (theta == "binary") {
    theta_low <-
      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
        z[, 5]
      )) * z[, 2]) ^ 2), size = 1)
    theta <-
      ifelse(theta_low == 1, 0.3, 0.1)
  } else if (theta == "big") {
    theta_big <-
      rbinom(N, pnorm((z[, 6] * (z[, 1] %*% t(
        z[, 5]
      )) * z[, 2]) ^ 2), size = 1)
    theta <- ifelse(theta_big == 1, 1, 0.4)
  }  else {
    theta == theta
  }

  g <- as.vector(cos(z %*% b) ^ 2)

  if(y=="binary") {
    y1 <- theta * d + g 
    y1.1 <- rbinom(N,prob=pnorm(scale(y1)),size=1)
    y <- y1.1
  } else {y <- theta * d + g + rnorm(N,0,var)}

  data <- as.data.frame(y)
  data <- cbind(data, theta, d, z)
  colnames(data) <- c("y", "theta", "d", c(paste0("V", 1:k)))

  return(data)
}

### Example
dataset <- datagen(y="binary",N = 2000, k = 20, random_d = F, theta = "binary", var = 1)
summary(dataset)
str(dataset)

glm(y ~ ., data = dataset, family = binomial(link = 'logit')) %>%
  summary()
```

```{r trash, eval = F}
dat_transform <- function(dat){
  # first make treatment indicator
  coefs <- runif(ncol(dat), -1, 1)

  # m/4 squared terms
  dat <- dat %>% 
    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))

  # m/4 exponentiated 
  dat <- dat %>% 
    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) exp(x)))

  # m/4 sin 
  dat <- dat %>% 
    mutate(across(sample(1:ncol(dat), m/4, replace = F), function(x) sin(x)))

  # m/2 2-way interactions
  dat <- bind_cols(dat,
    replicate(m/2, {
      index <- sample(1:m, 2, replace = F)
      dat[,index[1]] * dat[,index[2]]
      }, simplify = T))

  # m/4 3-way interactions
  dat <- bind_cols(dat,
    replicate(m/4, {
      index <- sample(1:m, 3, replace = F)
      dat[,index[1]] * dat[,index[2]] * dat[,index[3]]
      }, simplify = T))

  coefs <- runif(ncol(dat), -1, 1)

  y <- as.matrix(dat) %*% as.matrix(coefs)

  return(y)
}

sim_homemade <- function(m, n){
  m <- m-2
  dat <- replicate(m, rnorm(n, 0, 5)) %>%
    cbind(replicate(m/4, rbinom(n, 1, .5))) %>%
    as.data.frame()
  dat_original <- dat

  # first make treatment indicator
  dat <- data.frame(1, dat)
  coefs <- rnorm(ncol(dat), 0, 2)
  d <- round(1/(1+exp(-as.matrix(dat) %*% as.matrix(coefs))))

  dat <- data.frame(dat, d)

  # Set treatment effect to 2
  coefs <- c(rnorm(m+1, 0, 2), 2)
  y <- as.matrix(dat) %*% as.matrix(coefs) + rnorm(1)

  dat <- data.frame(dat, y)

  dat_new <- dat_original

  transformers <- rnorm(m, 0, 2)

  for(i in 1:m){
    dat_new[,i] <- dat_new[,i] * transformers[i]
  }

  # m/4 squared terms
  dat_new <- dat_new %>% 
    mutate(across(sample(1:m, m/4, replace = F), function(x) x^2))

  # m/4 exponentiated 
  dat_new <- dat_new %>% 
    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) exp(x)))

  # m/4 sin 
  dat_new <- dat_new %>% 
    mutate(across(sample(1:ncol(m), m/4, replace = F), function(x) sin(x)))

  # m/2 2-way interactions
  for(i in 1:round(m/2)){
    index <- sample(1:m, 2, replace = F)
    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]]
  }

  # m/4 3-way interactions
  for(i in 1:round(m/4)){
    index <- sample(1:m, 3, replace = F)
    dat_new[, index[1]] <- dat_new[,index[1]] * dat_new[,index[2]] * dat_new[,index[3]]
  }

  dat_final <- data.frame(dat_new, d = dat[,'d'], y = dat[,'y'])
  return(dat_final)
}

```{r functions}
## Pred functions ####
ols_logit_pred <- function(y, d, x){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  mu_mod <- lm(y ~  d + ., data.frame(y, d, x))
  mu1_pred <- predict(mu_mod, newdata = data.frame(y, d = 1, x))
  mu0_pred <- predict(mu_mod, newdata = data.frame(y, d = 0, x))

  pi_mod <- glm(d ~ ., data.frame(y, x), family = binomial(link = 'logit'))
  pi_pred <- predict(pi_mod, type = 'response')

  return(
    list(
      mu1_pred = mu1_pred, 
      mu0_pred = mu0_pred, 
      pi_pred = pi_pred,
      d = d,
      y = y
    ))
}

grf_pred <- function(y, d, x){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  forest_mu <- grf::regression_forest(X = data.frame(d, x), Y = y, 
                                 tune.parameters = "all")
  mu0_pred <- predict(forest_mu, newdata = data.frame(d = 0, x))$predictions
  mu1_pred <- predict(forest_mu, newdata = data.frame(d = 1, x))$predictions

  forest_pi <- grf::regression_forest(X = x, Y = d, tune.parameters = "all")
  pi_pred <- predict(forest_pi, newdata = x)$predictions

  return(
    list(
      mu1_pred = mu1_pred, 
      mu0_pred = mu0_pred, 
      pi_pred = pi_pred,
      d = d,
      y = y
    ))
}

superlearner_pred <- function(y, d, x, folds = 5, seed = 158){
  if('factor' %in% unlist(lapply(x, class))){
    x <- fastDummies::dummy_cols(x, remove_first_dummy = T, remove_selected_columns = T) 
  }

  set.seed(seed)
  mu_fit <- SuperLearner(
    Y = y,
    X = data.frame(d, x),
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family= gaussian()
  )

  pi_fit <- SuperLearner(
    Y = d,
    X = x,
    cvControl = list(V = folds),
    SL.library=c("SL.glm", 
                 "SL.glmnet", 
                 "SL.xgboost"),
    method="method.CC_nloglik", 
    family= binomial()
  )

  return(list(
    mu0_pred = as.numeric(predict(mu_fit, newdata = data.frame(d = 0, x), type = 'response')$library.predict %*% mu_fit$coef),
    mu1_pred = as.numeric(predict(mu_fit, newdata = data.frame(d = 1, x), type = 'response')$library.predict %*% mu_fit$coef),
    pi_pred = as.numeric(predict(pi_fit, type = 'response')$pred),
    d = d,
    y = y))
}

## Methods ####

lm_sim <- function(dat){
